### 2016-07-15 TreeLevel.tex
COMMITTED VERSION

\section{Squark and Gluino Production at Tree Level}\label{sec:SquarkGluinoTree}
This chapter considers the production of strongly interacting supersymmetric particles in the MRSSM.\footnote{In fact only the RSQCD is considered as contribution coming from the electroweak sector scale with $\mathcal{O(\alpha_w^2)}$ where $\alpha_w = \frac{g_w^2}{4\pi}$ or $\mathcal{O(\alpha_em^2)}$ where $\alpha_{\mathrm{em}} = \frac{e^2}{4\pi}$ and are therefore significantly smaller than contribution from the strongly interacting sector which scale with $\mathcal{O(\alpha_s^2)}$ where $\alpha_s = \frac{g_s^2}{4\pi}$.} The various processes and their associated cross sections are compared to their analogues in the MSSM.\\
The production of sgluons is not included in the following analysis. However, there are two possible channels for sgluon production at tree-level: a quark-antiquark and a gluon-gluon initiated process:
\begin{align}
q\overline{q} \to \phi_0\phi_0\ (\sigma_0\sigma_0), \hspace{2cm} GG \to \phi_0\phi_0\ (\sigma_0\sigma_0).
\end{align}
To give a reasonable and consistent prediction of hadronic cross sections, a scenario with large sgluon mass, i.e. soft breaking parameter $m_\sigma = \unit[5]{TeV}$, is considered. This validates the negligence of sgluon production as in this case they are too heavy to produce them significantly at the LHC with $\sqrt{S} = \unit[13]{TeV}$. See \cite{Choi:2008ub, GoncalvesNetto:2012nt, phdWojciech} for a calculation of the sgluon production cross section. \ignore{Feynman diagrams there are only ones, one can only produce sigma,sigma or phi,phi but not sigma,phi}Section \ref{sec:PartProcesses} gives analytic results for the parton reaction before the next section describes how the hadronic cross section is obtained. Section \ref{sec:tree-level_cross_sections} presents the hadronic cross section of all considered processes for various choices of squark and gluino mass. In particular, squark production is considered in detail. This includes the statement of uncertainties of the calculation.

@@

@@

The tree-level Feynman diagrams for squark and gluino production in the MRSSM are shown in fig. \ref{fig:TreeDiagrams}. On the partonic level there are six different channels. For squark-antisquark  and gluino-antigluino production there are two possible partonic reactions respectively.\\

@@

@@

\sigma^\mathrm{B}_{\mathrm{Had}}(P_1 P_2 \to X) = \int \mbox{d}x_1 \mbox{d}x_2\ f_{P_1/H_1}(x_1) f_{P_2/H_2}(x_2)\ \sigma^\mathrm{B}_{\mathrm{Part}} (P_1 P_2 \to X, s = x_ 1x_2 S).\label{eq:facTheorem}

@@

\begin{table}[H]
\begin{center}
\begin{tabular}{c?c|c|c}
\backslashbox{$m_{\tilde{g}}$}{$m_{\tilde{q}}$} & $\unit[500]{GeV}$ & $\unit[1000]{GeV}$ & $\unit[1500]{GeV}$\\
\hlinewd{2pt}
& & & \\
$\unit[1000]{GeV}$ & $\unit[934.9]{fb}\ _{- 27.2\%\ignore{735}- 2.1\% \ignore{915}}^{+ 30.0\% \ignore{1213}+ 1.2\% \ignore{946}}$ & $\unit[102.1]{fb}\ _{- 29.2\% \ignore{79.0}- 2.1\%\ignore{100}}^{+ 31.2\% \ignore{134}+ 1.9\% \ignore{104}}$ & $\unit[13.12]{fb}\ _{- 31.6\% \ignore{9.97}- 1.7\% \ignore{12.9}}^{+ 34.1\% \ignore{17.6}+ 2.1\% \ignore{13.4}}$\\
& & & \\
$\unit[1500]{GeV}$ & $\unit[360.9]{fb}\ _{- 30.0\% \ignore{282}- 2.2\% \ignore{353}}^{+ 30.5\% \ignore{471}+ 1.1\% \ignore{365}}$ & $\unit[50.52]{fb}\ _{- 29.5\% \ignore{39.0}- 1.9\% \ignore{49.6}}^{+ 32.4\% \ignore{66.9}+ 1.7\% \ignore{51.4}}$ & $\unit[7.712]{fb}\ _{- 31.8\% \ignore{5.85}- 2.8\% \ignore{7.5}}^{+ 34.9\% \ignore{10.4}+ 2.4\% \ignore{7.9}}$\\
& & & \\
$\unit[2000]{GeV}$ & $\unit[165.5]{fb}\ _{- 28.2\% \ignore{129}- 2.1\% \ignore{162}}^{+ 30.5\% \ignore{216}+ 0.9\% \ignore{167}}$ & $\unit[26.97]{fb}\ _{- 29.8\%\ignore{20.8}- 2.1\% \ignore{26.4}}^{+ 32.6\%\ignore{35.8} + 1.5\% \ignore{27.4}}$ & $\unit[4.625]{fb}\ _{- 31.8\% \ignore{3.51}- 1.6\% \ignore{4.55}}^{+ 34.5\% \ignore{6.22}+ 1.8\% \ignore{4.71}}$\\
\end{tabular}
\caption{Squark production cross section at tree-level (including five flavors and also the production of antisquarks) in the MRSSM for various squark and gluino masses. The parton density functions and the renormalization and factorization scale are chosen as in fig. \ref{fig:TreeXsection}. The uncertainty of the numerical integration is lower than one permille. The first relative uncertainty comes from the variation of $\mu_R$ and $\mu_F$ as described in the text. The second uncertainty corresponds to the parton density function uncertainty.}\label{tab:squarkMRSSM}
\end{center}
\end{table}
%\vspace{1cm}
\begin{table}[H]
\begin{center}
\begin{tabular}{c?c|c|c}
\backslashbox{$m_{\tilde{g}}$}{$m_{\tilde{q}}$} & $\unit[500]{GeV}$ & $\unit[1000]{GeV}$ & $\unit[1500]{GeV}$\\
\hlinewd{2pt}
& & & \\
$\unit[1000]{GeV}$ & $\unit[5257]{fb}\ _{- 24.6\% \ignore{4196}- 1.2\% \ignore{5163}}^{+ 28.4\% \ignore{6714}+ 1.8\% \ignore{5319}}$ 
& $\unit[340.4]{fb}\ _{- 28.4\% \ignore{265}- 1.9\% \ignore{334}}^{+ 31.0\% \ignore{446} + 1.6\% \ignore{346}}$ 
& $\unit[33.97]{fb}\ _{\- 30.6\% \ignore{26.0}- 1.2\%\ignore{33.5}}^{+ 33.6\% \ignore{45.4}+ 2.3\%\ignore{34.7}}$\\
& & & \\
$\unit[1500]{GeV}$ & $\unit[3263]{fb}\ _{- 25.4\% \ignore{2602}- 1.8\%\ignore{3205}}^{+ 27.9\%\ignore{4172}+ 1.2\%\ignore{3301}}$ 
& $\unit[260.7]{fb}\ _{- 28.4\%\ignore{203}- 2.2\%\ignore{255}}^{+ 30.8\% \ignore{341}+ 1.3\% \ignore{264}}$ 
& $\unit[30.46]{fb}\ _{- 30.7\%\ignore{23.3} - 1.9\%\ignore{29.9}}^{+  33.2\% \ignore{40.6} + 1.8\% \ignore{31.0}}$\\
& & & \\
$\unit[2000]{GeV}$ & $\unit[2179]{fb}\ _{- 25.6\% \ignore{1735}- 1.9\%\ignore{2139}}^{+ 27.9\% \ignore{2788}+ 1.1\%\ignore{2204}}$ 
& $\unit[198.1]{fb}\ ^{+ 30.7\%\ignore{259} + 1.5\%\ignore{201}}_{- 28.6\% \ignore{154}- 2.1\%\ignore{194}}$ 
& $\unit[25.75]{fb}\ ^{+ 33.2\%\ignore{34.3}+ 1.5\%\ignore{26.2}}_{- 30.7\% \ignore{19.7}- 2.0\%\ignore{25.3}}$\\
\end{tabular}
\caption{Same content as in table \ref{tab:squarkMRSSM} but for the MSSM.}
\end{center}
\end{table}

>>>>

\section{Squark and Gluino Production at Tree Level}\label{sec:SquarkGluinoTree}
This chapter considers the production of strongly interacting supersymmetric particles in the MRSSM.\footnote{In fact only the RSQCD is considered as contribution coming from the electroweak sector scale with $\mathcal{O}(\alpha_w^2)$ where $\alpha_w = \frac{g_w^2}{4\pi}$ or $\mathcal{O}(\alpha_{\mathrm{em}}^2)$ where $\alpha_{\mathrm{em}} = \frac{e^2}{4\pi}$ and are therefore significantly smaller than contribution from the strongly interacting sector which scale with $\mathcal{O}(\alpha_s^2)$ where $\alpha_s = \frac{g_s^2}{4\pi}$.} The various processes and their associated cross sections are compared to their analogues in the MSSM.\\
The production of sgluons is not included in the following analysis. However, there are two possible channels for sgluon production at tree-level: a quark-antiquark and a gluon-gluon initiated process:
\begin{align}
q\overline{q} \to \phi_0\phi_0\ (\sigma_0\sigma_0), \hspace{2cm} GG \to \phi_0\phi_0\ (\sigma_0\sigma_0).
\end{align}
To give a reasonable and consistent prediction of hadronic cross sections, a scenario with large sgluon mass, i.e. soft breaking parameter $m_\sigma = \unit[5]{TeV}$, is considered. This validates the negligence of sgluon production as in this case they are too heavy to produce them significantly at the LHC with $\sqrt{S} = \unit[13]{TeV}$. See \cite{Choi:2008ub, GoncalvesNetto:2012nt, phdWojciech} for a calculation of the sgluon production cross section. \ignore{Feynman diagrams there are only ones, one can only produce sigma,sigma or phi,phi but not sigma,phi}Section \ref{sec:PartProcesses} gives analytic results for the parton reaction before the next section describes how the hadronic cross section is obtained. Section \ref{sec:tree-level_cross_sections} presents the hadronic cross section of all considered processes for various choices of squark and gluino mass. In particular, squark production is considered in detail. This includes the statement of uncertainties of the calculation.

@@

The tree-level Feynman diagrams for squark and gluino production in the MRSSM are shown in fig. \ref{fig:TreeDiagrams}. On the partonic level there are six different channels. For squark-antisquark  and gluino-antigluino production there are two possible partonic reactions respectively.
\begin{figure}[H]

@@

\end{figure}\newpage

@@

\newpage

@@

\sigma^\mathrm{B}_{\mathrm{Had}}(P_1 P_2 \to X) = \int \mbox{d}x_1\  \mbox{d}x_2\ f_{P_1/H_1}(x_1) f_{P_2/H_2}(x_2)\ \sigma^\mathrm{B}_{\mathrm{Part}} (P_1 P_2 \to X, s = x_ 1x_2 S).\label{eq:facTheorem}

@@

\begin{table}[H]
\begin{tabular}{c?c|c|c}
\backslashbox{$m_{\tilde{g}}$}{$m_{\tilde{q}}$} & $\unit[500]{GeV}$ & $\unit[1000]{GeV}$ & $\unit[1500]{GeV}$\\
\hlinewd{2pt}
& & & \\
$\unit[1000]{GeV}$ & $\unit[934.9]{fb}\ _{- 27.2\%\ignore{735}- 2.1\% \ignore{915}}^{+ 30.0\% \ignore{1213}+ 1.2\% \ignore{946}}$ & $\unit[102.1]{fb}\ _{- 29.2\% \ignore{79.0}- 2.1\%\ignore{100}}^{+ 31.2\% \ignore{134}+ 1.9\% \ignore{104}}$ & $\unit[13.12]{fb}\ _{- 31.6\% \ignore{9.97}- 1.7\% \ignore{12.9}}^{+ 34.1\% \ignore{17.6}+ 2.1\% \ignore{13.4}}$\\
& & & \\
$\unit[1500]{GeV}$ & $\unit[360.9]{fb}\ _{- 30.0\% \ignore{282}- 2.2\% \ignore{353}}^{+ 30.5\% \ignore{471}+ 1.1\% \ignore{365}}$ & $\unit[50.52]{fb}\ _{- 29.5\% \ignore{39.0}- 1.9\% \ignore{49.6}}^{+ 32.4\% \ignore{66.9}+ 1.7\% \ignore{51.4}}$ & $\unit[7.712]{fb}\ _{- 31.8\% \ignore{5.85}- 2.8\% \ignore{7.5}}^{+ 34.9\% \ignore{10.4}+ 2.4\% \ignore{7.9}}$\\
& & & \\
$\unit[2000]{GeV}$ & $\unit[165.5]{fb}\ _{- 28.2\% \ignore{129}- 2.1\% \ignore{162}}^{+ 30.5\% \ignore{216}+ 0.9\% \ignore{167}}$ & $\unit[26.97]{fb}\ _{- 29.8\%\ignore{20.8}- 2.1\% \ignore{26.4}}^{+ 32.6\%\ignore{35.8} + 1.5\% \ignore{27.4}}$ & $\unit[4.625]{fb}\ _{- 31.8\% \ignore{3.51}- 1.6\% \ignore{4.55}}^{+ 34.5\% \ignore{6.22}+ 1.8\% \ignore{4.71}}$\\
\caption{Squark production cross section at tree-level (including five flavors and also the production of antisquarks) in the MRSSM for various squark and gluino masses. The parton density functions and the renormalization and factorization scale are chosen as in fig. \ref{fig:TreeXsection}. The uncertainty of the numerical integration is lower than one permille. The first relative uncertainty comes from the variation of $\mu_R$ and $\mu_F$ as described in the text. The second uncertainty corresponds to the parton density function uncertainty.}\label{tab:squarkMRSSM}
%\vspace{1cm}
\begin{table}[H]
\begin{tabular}{c?c|c|c}
\backslashbox{$m_{\tilde{g}}$}{$m_{\tilde{q}}$} & $\unit[500]{GeV}$ & $\unit[1000]{GeV}$ & $\unit[1500]{GeV}$\\
\hlinewd{2pt}
& & & \\
$\unit[1000]{GeV}$ & $\unit[5257]{fb}\ _{- 24.6\% \ignore{4196}- 1.2\% \ignore{5163}}^{+ 28.4\% \ignore{6714}+ 1.8\% \ignore{5319}}$ 
& $\unit[340.4]{fb}\ _{- 28.4\% \ignore{265}- 1.9\% \ignore{334}}^{+ 31.0\% \ignore{446} + 1.6\% \ignore{346}}$ 
& $\unit[33.97]{fb}\ _{\- 30.6\% \ignore{26.0}- 1.2\%\ignore{33.5}}^{+ 33.6\% \ignore{45.4}+ 2.3\%\ignore{34.7}}$\\
& & & \\
$\unit[1500]{GeV}$ & $\unit[3263]{fb}\ _{- 25.4\% \ignore{2602}- 1.8\%\ignore{3205}}^{+ 27.9\%\ignore{4172}+ 1.2\%\ignore{3301}}$ 
& $\unit[260.7]{fb}\ _{- 28.4\%\ignore{203}- 2.2\%\ignore{255}}^{+ 30.8\% \ignore{341}+ 1.3\% \ignore{264}}$ 
& $\unit[30.46]{fb}\ _{- 30.7\%\ignore{23.3} - 1.9\%\ignore{29.9}}^{+  33.2\% \ignore{40.6} + 1.8\% \ignore{31.0}}$\\
& & & \\
$\unit[2000]{GeV}$ & $\unit[2179]{fb}\ _{- 25.6\% \ignore{1735}- 1.9\%\ignore{2139}}^{+ 27.9\% \ignore{2788}+ 1.1\%\ignore{2204}}$ 
& $\unit[198.1]{fb}\ ^{+ 30.7\%\ignore{259} + 1.5\%\ignore{201}}_{- 28.6\% \ignore{154}- 2.1\%\ignore{194}}$ 
& $\unit[25.75]{fb}\ ^{+ 33.2\%\ignore{34.3}+ 1.5\%\ignore{26.2}}_{- 30.7\% \ignore{19.7}- 2.0\%\ignore{25.3}}$\\
\caption{Same content as in table \ref{tab:squarkMRSSM} but for the MSSM.}\label{tab:zweite}
The cross sections for the production of squarks (and antisquarks) including five flavors are given for a representative set of masses in table \ref{tab:squarkMRSSM} for the MRSSM and in table \ref{tab:zweite} for the MSSM. In addition to the cross section, the relative uncertainty of the scale variation and the parton density functions are given.\\

### 2016-07-15 Virt_Real.tex
COMMITTED VERSION

According to quantum field theory the $\mathcal{O}(\alpha_s)$ correction to a tree-level process includes the computation of one-loop diagrams such as shown in fig. \ref{fig:1loopdiagrams}. To yield $\mathcal{O}(\alpha_s)$ corrections in the cross section, the interference term between the one-loop amplitude $\mathcal{M}^{\mathrm{1L}}$ and the Born amplitude $\mathcal{M}^{\mathrm{B}}$ needs to be considered: 

@@

@@

where $\sigma^{\mathrm{R}}$ denotes the cross section arising from real corrections. However, real corrections also contain divergences. To see how these arise, consider the second diagram in fig. \ref{fig:RealGluon}. The propagator of the quark which radiates off a gluon gives a contribution of the form
Including these singularities into the cross section causes the cancellation of single poles coming from the virtual cross section and the soft divergences coming from the real cross section as well as the cancellation of double poles. At this point the only singularities which are left in the sum of real and virtual cross section are collinear ones, coming from the real correction.

@@

\end{figure}\\

@@

Here, the indices $P_i$ label partons, i.e. quarks or the gluon, and $H$ labels the hadron in which the partons are confined. $\Gamma(\hdots)$ is the Gamma function and $P_{P_i P_j}(x)$ are the Altarelli-Parisi-kernels\cite{Altarelli:1977zs} which are a measure for the propability of finding a parton $P_i$ with momentum fraction $x$ within a parton $P_j$. This procedure of removing collinear divergences is referred to as mass factorization \cite{dissertori2003quantum}.\\

>>>>

According to quantum field theory the $\mathcal{O}(\alpha_s)$ correction to a tree-level process includes the computation of one-loop diagrams such as shown in fig. \ref{fig:1loopdiagrams}. 

@@

To yield $\mathcal{O}(\alpha_s)$ corrections in the cross section, the interference term between the one-loop amplitude $\mathcal{M}^{\mathrm{1L}}$ and the Born amplitude $\mathcal{M}^{\mathrm{B}}$ needs to be considered: 

@@

where $\sigma^{\mathrm{R}}$ denotes the cross section arising from real corrections. However, real corrections also contain divergences. To see how these arise, consider the second diagram in fig. \ref{fig:RealGluon}.

@@

The propagator of the quark which radiates off a gluon gives a contribution of the form
Including these singularities into the cross section causes the cancellation of single poles coming from the virtual cross section and the soft divergences coming from the real cross section as well as the cancellation of double poles. At this point the only singularities which are left in the sum of real and virtual cross section are collinear ones, coming from the real correction.\\

@@

Here, the indices $P_i$ label partons, i.e. quarks or the gluon, and $H$ labels the hadron in which the partons are confined. $\Gamma(\hdots)$ is the Gamma function and $P_{P_i P_j}(x)$ are the Altarelli-Parisi-kernels\cite{Altarelli:1977zs} which are a measure for the propability of finding a parton $P_i$ with momentum fraction $x$ within a parton $P_j$. This procedure of removing collinear divergences is referred to as mass factorization \cite{dissertori2003quantum}.
